rgbif: a package for working with species occurrence data in R

### 2015-10-04 manuscript.Rmd
tweaks
manuscript edits, ignore git_deploy scritpt for now

Herein, we describe a library for working with GBIF data in
the R programming environment [@R]. R is an extremely widely used
language in academia, non-profits, and the private sector.
Importantly, R make it easy to do all of the steps of the
research process, including data management, data manipulation
and cleaning, statistics, and vizualization. An R client
for getting GBIF is a powerful tool for reproducible research.

@@

```{r}
"xxx"
```

@@

@@

@@

`rgbif` ...

>>>>

Herein, we describe a library (rgbif [@rgbif]) for working with
GBIF data in the R programming environment [@R]. R is an extremely
widely used language in academia, non-profits, and the private sector.
Importantly, R make it easy to do all of the steps of the
research process, including data management, data manipulation
and cleaning, statistics, and vizualization. An R client
for getting GBIF is a powerful tool for reproducible research.

@@

The GBIF reqistry API services are spread across four major sets
of functions:

* Datasets
* Installations
* Networks
* Nodes
* Organizations

### Datasets

Search for datasets

```{r}
dataset_search(keyword="france", return = "data")
```

Get dataset metrics

```{r}
res <- dataset_metrics(uuid='66dd0960-2d7d-46ee-a491-87b9adcfe7b1')
data.frame(names(res$countByRank), unname(unlist(res$countByRank)))
```

### Networks, nodes, and installations

Here, we search for the first give GBIF networks, returning just the
key and title fields.

```{r}
networks(limit=5)$data[ , c('key', 'title')]
```

@@

GBIF provides two ways to get occurrence data: through the
/occurrence/search route (see `occ_search`), or via the
/occurrence/download route (many functions, see below).
`occ_search` is more appropriate for smaller data, while
occ_download*() functions are more appropriate for larger
data requests.

@@

The download API syntax is similar to the occurrence search API
in that the same parameters are used, but the syntas is quite different.
For example, in the download API you can do greater than searches,
whereas you can not do that in the occurrence search API.

```{r}
occ_download_get("0000066-140928181241064", overwrite = TRUE)
```

@@
